Kronos \& Krios: Evidence for accretion of massive, rocky planetary system in a sun-like pair

### 2017-06-06 paper/ms.tex
Use present tense throughout summary sec.; other grammar, wording edits.

We have reported and discussed the discovery of a comoving pair of bright
solar-type stars HD~240430 and HD~240429 (G0 and G2) with very different
metallicities ($\Delta\feh \approx 0.2$~dex), and a condensation temperature
(\Tcondens)-dependent abundance differences.
The more metal-rich of the two, HD~240430 (\bizarreone), show enhancement in
all ten elements with $\Tcondens > 1200$~K including \elem{Fe}, while under
enhanced in the five elements, \elem{C}, \elem{N}, \elem{O}, \elem{Na}, and
\elem{Mn} with $\Tcondens < 1200$~K relative to HD~240429 (\sunanalog).
The two stars also have anomalously high surface \elem{Li} abundance compared
to their ages of $\sim 4$~Gyr.
We considered that the comoving pair may have formed from two stars of different
birth origins in a exchange scattering event, or that there may be chemical
inhomogeneity in the birth cloud to find both unlikely.

In order to explain the $\Tcondens$-dependent enhancement and high \elem{Li}
abundance, we considered accretion of planetary material due to e.g., dynamical
instability in some detail.
We have argued that a recent accretion of $20$~\mearth\ of bulk Earth
composition to \bizarreone\ can explain the enhancement in both refractory
elements and the \elem{Li}.
For \sunanalog\ which also has high surface \elem{Li} abundance given its age,
we put an upper limit of $\approx 4$~\mearth\ on the accreted mass
based on the \elem{Li} concentration of carbonaceous chondrites and bulk Earth.
While the case is not as clear as \bizarreone\ without a chemical reference star,
the range of abundances from volatile to refractory elements is
similar to that expected from $\approx 4$~\mearth\ accretion of bulk Earth.
It is unclear what triggered the accretions to both stars.
A possiblity is that a fly-by field star might have
perturbed the planetary systems of both stars.

The two stars have not been included in any planet search programs
by high-precision radial velocity or transit method.
In case that there indeed were accretions to both stars as we
have argued, it will be interesting to see the architectures
of the planetary systems left behind, and whether
they are very different betweeen the two stars.

% somewhat of a rant that can be removed ...
The investigation and conclusion on this puzzling comoving pair, like any other
problem, depends strongly on one's prior belief.
A difference of $\approx 0.2$~dex in \feh\ may enough for one to conclude that
the two stars are unrelated and their proximity in phase space is by chance.
On the other hand, if one has a stronger prior belief that two stars in such
proximity in phase space ought to be of the same birth origin, and thus
must have had near-identical chemical compisiton at birth, an engulment of
refractory-rich planetary material provides an explanation for their
$\Tcondens$-dependent abundance difference.

>>>>

We report the discovery of a comoving pair of bright
solar-type stars HD~240430 and HD~240429 (G0 and G2) with very different
metallicities ($\Delta\feh \approx 0.2$~dex), and condensation temperature
(\Tcondens)-dependent abundance differences.
The more metal-rich of the two stars, HD~240430 (\bizarreone), shows enhancement in
all ten elements with $\Tcondens > 1200$~K including \elem{Fe}, while under
enhanced in the five elements, \elem{C}, \elem{N}, \elem{O}, \elem{Na}, and
\elem{Mn} with $\Tcondens < 1200$~K relative to HD~240429 (\sunanalog).
The two stars also have anomalously high surface \elem{Li} abundance compared
to their ages of $\sim 4$~Gyr.
We consider that the comoving pair may have formed from two stars of different
birth origins in a exchange scattering event, or that there may be chemical
inhomogeneity in the birth cloud, and find both unlikely.

In order to explain the $\Tcondens$-dependent enhancement and high \elem{Li}
abundance, we consider accretion of planetary material as the cause.
We argue that a recent accretion of $20$~\mearth\ of bulk Earth
composition to \bizarreone\ can explain the enhancement in both refractory
elements and the \elem{Li}.
For \sunanalog\ which also has high surface \elem{Li} abundance given its age,
we put an upper limit of $\approx 4$~\mearth\ on the accreted mass
based on the \elem{Li} concentration of carbonaceous chondrites and bulk Earth.
While the case is not as clear as \bizarreone\ without a chemical reference star,
the range of abundances from volatile to refractory elements is
similar to that expected from $\approx 4$~\mearth\ accretion of bulk Earth.
It is unclear what triggered the accretions to both stars.
One possibility is that a fly-by field star may have
perturbed the planetary systems of both stars.

The two stars have not been included in any publicly released data from planet
search programs.
If both stars have accreted planetary material, it would be very interesting to
search for the existence and architectures of the planetary systems left
behind, and whether they are very different between the two stars.

% somewhat of a rant that can be removed ...
The investigation and conclusion on this puzzling comoving pair, like any other
problem, depends strongly on one's prior belief.
A difference of $\approx 0.2$~dex in \feh\ may enough for one to conclude that
the two stars are unrelated and their proximity in phase space is by chance.
On the other hand, if one has a stronger prior belief that two stars in such
proximity in phase space ought to be of the same birth origin, and thus
must have had near-identical chemical composition at birth, an engulfment of
refractory-rich planetary material provides an explanation for their
$\Tcondens$-dependent abundance difference.
